Photographic Text-to-Image Synthesis \\ with a Hierarchically-nested Adversarial Network

### 2017-11-15 cvpr2018.tex
almostfinal

%%%%%%%%% BODY TEXT
\section{Introduction}
Photographic text-to-image synthesis is a significant problem in generative model research \cite{reed2016generative}, which aims to learn a mapping from a semantic text space to a complex RGB image space. This task requires the generated images to be not only realistic but also \textit{semantically consistent}, i.e., the generated images preserve the object color and sketch described in text and fine-grained descriptive details in image pixels as well.

@@

%\begin{figure}[t]
%	\centering
%	\includegraphics[width=0.4\textwidth]{figure/intro.pdf}
%	\vspace{-.3cm}
%	\caption{Overview of our hierarchically-nested adversarial network. It contains a single-stream generator and several nested discriminators along the depth dimension of the generator, which can generate high-resolution images conditioned on a sentence.} \label{fig:archs-review} \vspace{-.3cm}
%\end{figure}
%\begin{figure}[t]
%	\centering
%	\includegraphics[width=0.4\textwidth]{figure/single_view.pdf}
%	\vspace{-.3cm}
%	\caption{Overview of our hierarchically-nested adversarial network. It contains a single-stream generator and several nested discriminators along the depth dimension of the generator, which can generate high-resolution images conditioned on a sentence.} \label{fig:archs-review} \vspace{-.3cm}
%\end{figure}
Recently, generative adversarial networks (GANs) have become the main solution to this task. 
Reed \etal \cite{reed2016generative} address this task through a GAN based framework. But this method only scale up to $64^2$ resolution and can barely generate vivid object details.
Based on this method, StackGAN  \cite{han2017stackgan} is a successful approach, which stacks another low-to-high resolution GAN to generate high-resolution $256^2$ images in a two-stage training strategy. Later on, \cite{dong2017semantic} proposes to bypass the difficult of learning a mapping from text to RGB images and treat it as a pixel-to-pixel translation problem \cite{isola2016image}. It works by re-rendering an arbitrary-style $128^2$ training  image conditioned on a targeting description. However, its high-resolution synthesis capability is still unclear. 
At present, training a generative model to map from a low-dimensional text space to a high-resolution image space in a fully end-to-end manner still remains unsolved.

This paper pays attention to two major difficulties for text-to-image synthesis using GANs. The first is balancing the convergence between generators and discriminators \cite{goodfellow2014generative,improvedGAN}, which is actually a long-term problem in GANs. The second is stably modeling the huge pixel space in high-resolution images and guaranteeing semantic consistency \cite{han2017stackgan}. 
An effective strategy to regularize generators is critical to stabilize the training and help capture the complex image statistics \cite{huang2016stacked}.

@@

Our generator resembles a simple vanilla GAN, without requiring any multiple internal text conditioning like \cite{han2017stackgan} or outside image annotation supervision like \cite{dash2017tac}. To tackle the problem of the big leap from the text space to the high-resolution image space, our insight is to leverage and regularize hierarchical representations with additional `deep' adversarial constraints. 
We introduce accompanying hierarchically-nested discriminators at multi-scale intermediate layers to play adversarial games and jointly encourage the generator approaching the real training data distribution. 
We also propose a new convolutional neural network (CNN) design for the generator to support accompanied discriminators more effectively in an end-to-end training manner.
To guarantee the image diversity and semantic consistency,
we enforce discriminators at scale-different generator side outputs to simultaneously differentiate real-and-fake image-text pairs as well as real-and-fake
local image patches.

@@

We validate our proposed method on three datasets, CUB birds \cite{welinder2010caltech}, Oxford-102 flowers \cite{Nilsback08}, and large-scale MSCOCO \cite{lin2014microsoft}. In complement of existing evaluation metric (e.g. Inception score \cite{improvedGAN}) for generative models, we also introduce a new visual-semantic similarity metric to evaluate the alignment between generated images and conditioned text. Extensive experimental results and analysis demonstrate the effectiveness of our method and significantly improved performance compared against previous state of the arts on three metrics.

@@

\section{Related Work}
We discussed related work and further clarify the novelty of our method by comparing with them.

@@

Text-to-image synthesis is a significant problem in GANs. Reed \etal \cite{reed2016generative}  is the first to introduce a method that can generate $64^2$ resolution images, which is similar with DCGAN \cite{radford2015unsupervised}. This method presents a new strategy for image-text matching aware adversarial training. Reed \etal \cite{reed2016learning} propose a generative
adversarial what-where network (GAWWN) to enable location and content instructions in text-to-image synthesis. StackGAN \etal \cite{han2017stackgan} propose a two-stage stacking GAN training approach that is able to generate $256^2$ compelling images. Recently, Dong \etal \cite{dong2017semantic} propose to learn a joint embedding of images and text so as to re-render a prototype image conditioned on a targeting description. Cha \etal \cite{char2017perceptual} explore the usage of the perceptional loss \cite{johnson2016perceptual} with a CNN pretrained on ImageNet  and Dash \etal \cite{dash2017tac} make use of auxiliary classifiers (similar with \cite{odena2016conditional}) to assist GAN training for text-to-image synthesis.

Learning a continuous mapping from a low-dimensional embedding manifold to a complex real data distribution is a long-standing problem. Although GANs have made significant progress, there are still many unsolved difficulties, e.g. training instability and high-resolution generation. Wide methods have been proposed to address the training instability, such as various training techniques \cite{salimans2016improved,arjovsky2017wasserstein,berthelot2017began,shrivastava2016learning,odena2016conditional}, regularization using extra knowledge (e.g. image labels, ImageNet CNNs, etc) \cite{dosovitskiy2016generating,ledig2016photo,dash2017tac,dash2017tac}, or different generator and discriminator combinations  \cite{metz2016unrolled,durugkar2016generative,yang2017lr,huang2016stacked}. \textit{While our method shows a new way to unite generators and discriminators and does not requires any extra knowledge apart from training paired text and images.} Additionally, it is easy to see the training difficulty increases significantly as the targeting image resolution increases.

@@

To synthesize high-resolution images, cascade networks are effective to decompose originally difficult tasks to multiple subtasks (Figure \ref{fig:archs-review} A).
Denton \etal \cite{denton2015deep} train a cascade of GANs in a Laplacian pyramid framework (LAPGAN) and use each to synthesize and refine image details and push up the output resolution stage-by-stage. StackGAN also shares some similar idea with LAPGAN. Inspired by this strategy, Chen \etal \cite{chen2017photographic} present a cascaded refinement network to synthesize high-resolution scene from semantic maps. 
%%% Huang \etal \cite{huang2016stacked} propose a top-down stacked GAN to leverage mid-level representations, which shares some similarities with StackGAN and our method. However, this method needs multiple symmetric bottom-up pre-trained discriminators and the usage for high-resolution image is unclear. 
Recently, Karras \etal \cite{Karras2017progressive} propose a progressive training of GANs. The idea is adding symmetric generator and discriminator layers gradually for high-resolution image generation (Figure \ref{fig:archs-review} C). \textit{Compared with these strategies that train low-to-high resolution GANs stage-by-stage or progressively, our method has the advantage of leveraging mid-level representations to encourage implicit subtask integration, which makes end-to-end high-resolution image synthesis in a single vanilla-like GAN possible.}

@@

\subsection{Adversarial objective basics}
In brief, a GAN \cite{goodfellow2014generative} consists of a generator $G$ network and a discriminator $D$ network, which are playing an adversarial game to compete with each other. The discriminator is optimized to distinguish synthesized images from real images, meanwhile the generator is optimized to generate fake images to fool the discriminator. Concretely, the overall min-max optimization objective is defined as: 
\begin{equation}
\label{equ:GAN}
\begin{split}
G^*, D^* = \arg~\underset{G}{\min}\ \underset{D}{\max}~ \mathcal{V}(D, G, Y, \bm z),
\end{split}
\end{equation}
where $Y$ and $\bm z \sim \mathcal{N}(0,1)$ denote training images and random noises, respectively. 
%$G$ is learned to approximate $G(\bm z) \sim p(Y)$.  The loss $\mathcal{L}$ for the valuation function is usually a cross-entropy loss, such that $\mathcal{V}(\cdot) = - \mathcal{L}(\cdot)$. 
$\mathcal{V}$ is the overall GAN objective, which usually takes the (cross-entropy loss) form $\mathbb{E}_{Y\sim p_{data}}\big[\log D(Y)\big] + \mathbb{E}_{\bm z\sim p_{z}}\big[\log (1-D(G(\bm z)))\big]$ or other variations \cite{lsgan,berthelot2017began}.

@@

The proposed $\mathcal{G}$ is a CNN (defined in Section 3.4) with multiple resolution-growing side outputs:
%This architecture resemble the proposed inverse architectures in edge detection\cite{xie2015holistically} and classification \cite{lee2015deeply}, which demonstrate that additional supervision to hidden layers can improve model generalization and boost optimization.  
\begin{equation}
\label{side}
X_1,..., X_s = \mathcal{G}(\bm t, \bm z), 
\end{equation}
where  $\bm t\sim p_{data}$ denotes a sentence embedding vector in the real training data distribution (generated by a pre-trained char RNN encoder). $\{X_1,...,X_{s-1}\}$ are resolution-growing images and $X_s$ is the final output with the highest resolution.

@@

For each side output $X_i$ from the generator, a distinct discriminator $D_i$ is associated to compete with it. Therefore, our full min-max objective is defined as 
\begin{equation}
\label{equ:optim}
\begin{split}
  \mathcal{G}^*, \mathcal{D}^*&  =  \arg~\underset{\mathcal{G}}{\min}\ \underset{\mathcal{D}}{\max}~ \mathcal{V}(\mathcal{G},\mathcal{D}, \mathcal{Y}, \bm t, \bm z), \\
  %\text{where} \;\;	 \mathcal{D} & =  \{D_1, ..., D_s\}, \; \mathcal{Y} = \{Y_1, ..., Y_s\},
\end{split}
\end{equation}
where $\mathcal{D}  =  \{D_1, ..., D_s\} $ and $\; \mathcal{Y} = \{Y_1, ..., Y_s\}$ is a set of training images at multi-scales, $\{1,...,s\}$.
Compared with Eq. (\ref{equ:GAN}), one generator competes with multiple discriminators  $\{D_i\}$ at different hierarchies (Figure \ref{fig:archs-review} D), which learn discriminative features in different contextual scales, respectively.

In principle, the lower-resolution side output is used to learn semantic consistent image structures (e.g. object sketches, colors, and background), and the subsequent higher-resolution side outputs are used to render fine-grained details. Since our method is trained in an end-to-end manner, the lower-resolution side outputs can fully enjoy the top-down knowledge from higher resolutions, such that we can observe consistent image structures and styles appear in both low and high resolutions.
The experiment demonstrates this advantage compared with StackGAN. 
% % According to our empirical observation, our design is able to reduce the model instability, especially at the early stage of the training.

%% %We present the following multi-purpose adversarial loss to support more effective generator training.

\subsection{Multi-purpose adversarial losses}
Our generator produces resolution-growing side outputs, which compose an image pyramid. 
We leverage this hierarchy property and allow adversarial losses to capture different statistics, with a goal to guarantee both semantic consistency and image fidelity.

In order to guarantee semantic consistency, we adopt the matching-aware pair loss proposed by \cite{reed2016generative}. The discriminator is designed to take image-text pairs as inputs and be trained to differentiate two types of errors: a real image with mismatched text and a fake image with conditioned text.

The pair loss is designed to guarantee the global semantic consistency. However, there lacks an explicit loss that forces the discriminator to differentiate real images from fake images. And combining both tasks (generating realistic images and matching image styles with text) into one loss complicates the already challenging learning tasks. Moreover, as the image resolution goes higher, it might be challenging for a global pair-loss discriminator to capture the local fine-grained details (results are validated in experiments).
%As the image resolution goes higher, discriminators might loss focus for local fine-grained image details.
%However, this loss has two major weaknesses. First, there is no explicit loss that force the discriminator to differentiate real images from fake images. 
%Combining both tasks (generating realistic images and matching image with text) into one output further complicates the learning tasks, which is already challenging. 
%Second, as the image resolution goes higher, it might be challenging for a global pair-loss discriminator to capture local fine-grained details.  
In addition, as pointed in \cite{shrivastava2016learning}, a single global discriminator may over-emphasize certain biased local features and lead to artifacts.

To alleviate these issues and guarantee image fidelity, our solution is to add local adversarial image losses.
%as inspired by \cite{shrivastava2016learning}. 
%The insights are two folds:
%\begin{itemize}\vspace{-.1cm}
%\setlength\itemsep{-0.3em}
%\item Further forcing the generated samples to have only only global but also local similar statistics to real image patches, which is beneficial for rendering fine-grained details. 
%
%\item \textcolor{red}{Image loss without using paired text can be beneficial in the sense that it focus more on image information. The richness of discriminator supervision usually has advantages for generalization. } 
%\vspace{-.2cm}
%\end{itemize}
We expect the low-resolution discriminator to focus on global structures, while the high-resolution discriminator to focus  on local image details.
Each discriminator consists of two branches (see Section 3.4), one computes a single scalar value for the pair loss and another branch computes a $R{\times}R$ probability map. 
Each location differentiates whether an overlapping image patch is real or fake.
Through the pyramid of the size-growing side outputs, we control $R$ accordingly. Specifically, a larger $R$ value results in a smaller local range and finer focus of discriminators.
The local image adversarial loss can be implemented as an fully CNN \cite{shrivastava2016learning,zhu2017unpaired,isola2016image}.
Figure \ref{fig:loss} illustrates how hierarchically-nested discriminators compute the two losses on the generated images in the pyramid.

\begin{figure}[t]
	\centering
	\includegraphics[width=0.49\textwidth]{figure/loss.pdf}
	\vspace{-.7cm}
	\caption{Given a set of images from the side output pyramid of the generator, the corresponding discriminator $D_i$ computes the matching-aware pair loss and local image loss (outputting a $R{\times}R$ probability map to classify real or fake image patches). $R$ increases as the image size grows. }  \vspace{-.2cm}
	\label{fig:loss}
\end{figure}

\textbf{Full Objective } Overall, our full min-max adversarial objective is defined as 
%%hierarchically-nested discriminators $\{D_i\}$ optimize the following objective:
\vspace{-.2cm}
\begin{equation}
\begin{split}
\mathcal{V}(& \mathcal{G},\mathcal{D}, \mathcal{Y}, \bm t, \bm z) = \sum_{i=1}^{s} \Big(  L_2\big(D_i({Y}_i)\big) +  L_2\big(D_i({Y}_i, \bm t_{Y})\big) \, + \\ 
& \overline{L_2}\big(D_i({X}_i)\big)  + \overline{L_2}\big(D_i({X}_i, \bm{t}_{X_i})\big) + \overline{L_2}\big(D_i({Y}_i,  \bm{t}_{\overline{Y}})\big) \Big),
\end{split}
\end{equation}
where $L_2(x) = \mathbb{E}\big[(x - \mathbb{I})^2\big]$ is the mean-square loss (instead of the conventional cross-entropy loss) and $\overline{L_2}(x) =\mathbb{E}\big[x^2\big]$. 
This objective is maximized by $\mathcal{D}$. While for $\mathcal{G}$ practically, we minimize 
$\sum_{i=1}^{s} (L_2(D_i(\mathcal{G}(\bm t, \bm z)_i)) +  L_2\big(D_i(\mathcal{G}(\bm t, \bm z)_i, \bm{t}_{X_i})))$.
For the local image loss, the shape of $x, \mathbb{I} \in \mathbb{R}^{R{\times}R}$ vary accordingly (see Figure \ref{fig:loss}). $R=1$ refers to the (largest local) global range. $D_i(X_i)$ is the image loss branch and $D_i(X_i, \bm{t}_{X_i})$ is the pair loss branch (conditioned on $\bm{t}_{X_i}$).
$\{Y_i, \bm t_{Y}\}$ denotes a matched image-text pair and $\{Y_i, \bm{t}_{\overline{Y}}\}$ denotes a mismatched image-text pair.

In the spirit of variational auto-encoder \cite{vae} and the practice of StackGAN \cite{han2017stackgan} (namely conditioning augmentation (CA)), instead of directly using deterministic text embedding, we sample a stochastic vector from a Ganssian distribution $\mathcal{N}(\mu({\bm t}), \Sigma({\bm t}))$, where $\mu$ and $\Sigma$ are parameterized functions of $\bm t$. 
We add the Kullback-Leibler divergence regularization term, $D_{KL}(\mathcal{N}(\mu({\bm t}), \Sigma({\bm t}) )|| \mathcal{N}(0, \bm{I}))$ \cite{vae}, to $\mathcal{G}$ loss to prevent over-fitting and force smooth sampling over the text embedding distribution.

@@

\textbf{Generator} The generator is simply composed by three kinds of modules, termed as $K$-repeat res-blocks, stretching layers, and linear compression layers.
A single res-block in the $K$-repeat res-block is a modified\footnote{We remove ReLU after the skip-addition of each residual block, with an intention to reduce sparse gradients.} residual block \cite{he2016identity}, which contains two convolutional (conv) layers (with batch normalization (BN) \cite{ioffe2015batch} and ReLU). The stretching layer serves to change the feature map size and dimension. It simply contains a scale-$2$ nearest up-sampling layer followed by a conv layer with BN+ReLU. The linear compression layer is a single conv layer followed by a Tanh to directly compress feature maps to the RGB space (as side outputs). We prevent any non-linear function in the compression layer that could impede the gradient signals. 
%, whose compact design enforces feature maps in conv blocks can linearly represent RGB images at arbitrary scales.
Starting from a $1024{\times}4{\times}4$ embedding, which is computed by CA and a trained embedding matrix, the generator simply uses $M$ $K$-repeat res-blocks connected by $M{-}1$ in-between stretching layers until the feature maps reach to the targeting resolution. 
For example, for $256{\times}256$ resolution and $K{=}1$, there are $M{=}6$ $1$-repeat res-blocks and $5$ stretching layers. 
%Such simple and symmetric design makes our generator helpful for gradient flows. We will verify in experiments. 
At pre-defined side-output positions at scales $\{1,...,s\}$, we apply the compression layer to generate side output images, for the input of the discriminator.

>>>>

%%%%%%%%% BODY TEXT
\section{Introduction}
Photographic text-to-image synthesis is a significant problem in generative model research \cite{reed2016generative}, which aims to learn a mapping from a semantic text space to a complex RGB image space. This task requires the generated images to be not only realistic but also \textit{semantically consistent}, For example, the generated images should preserve the object shape and color information described in the text.

%the generated images preserve the object color and sketch described in text and fine-grained descriptive details in image pixels as well.

@@

%\begin{figure}[t]
%	\centering
%	\includegraphics[width=0.4\textwidth]{figure/intro.pdf}
%	\vspace{-.3cm}
%	\caption{Overview of our hierarchically-nested adversarial network. It contains a single-stream generator and several nested discriminators along the depth dimension of the generator, which can generate high-resolution images conditioned on a sentence.} \label{fig:archs-review} \vspace{-.3cm}
%\end{figure}
%\begin{figure}[t]
%	\centering
%	\includegraphics[width=0.4\textwidth]{figure/single_view.pdf}
%	\vspace{-.3cm}
%	\caption{Overview of our hierarchically-nested adversarial network. It contains a single-stream generator and several nested discriminators along the depth dimension of the generator, which can generate high-resolution images conditioned on a sentence.} \label{fig:archs-review} \vspace{-.3cm}
%\end{figure}
Recently, Generative adversarial networks (GANs) have become the main solution to this task. 
Reed \etal \cite{reed2016generative} address this task through a GAN based framework. But this method only scales up to $64^2$ resolution and can barely generate vivid object details.
Based on this method, StackGAN  \cite{han2017stackgan} propose a two-stage training strategy to generate high-resolution $256^2$ images. But this methods requires training two separate GANs.  Later on, \cite{dong2017semantic} proposes to bypass the difficulty of learning mappings from vector embeddings to RGB images and treat it as a pixel-to-pixel translation problem \cite{isola2016image}. It works by re-rendering an arbitrary-style $128^2$ training image conditioned on a targeting description. However, its high-resolution synthesis capability remains unclear.

This paper pays attention to two major difficulties for text-to-image synthesis with GANs. The first is balancing the convergence between generators and discriminators \cite{goodfellow2014generative,improvedGAN}, which is actually a long-term problem in GANs. The second is stably modeling the huge pixel space in high-resolution images and guaranteeing semantic consistency \cite{han2017stackgan}. 
An effective strategy to regularize generators is critical to stabilize the training and help capture the complex image statistics \cite{huang2016stacked}.

@@

Our generator resembles a simple vanilla GAN, without without requiring multi-stage training and multiple internal text conditioning like \cite{han2017stackgan} or additional class label supervision like \cite{dash2017tac}. To tackle the problem of the big leap from the text space to the high-resolution image space, our insight is to leverage and regularize hierarchical representations with additional `deep' adversarial constraints. 
We introduce accompanying hierarchically-nested discriminators at multi-scale intermediate layers to play adversarial games and jointly encourage the generator approaching the real training data distribution. 
We also propose a new convolutional neural network (CNN) design for the generator to support accompanying discriminators more effectively in an end-to-end training manner.
To guarantee the image diversity and semantic consistency, we enforce discriminators at multiple side outputs of the generator to simultaneously differentiate real-and-fake image-text pairs as well as real-and-fake local image patches. %For more details, please refer to Section~\ref{sec:localloss}%focal

@@

We validate our proposed method on three datasets, CUB birds \cite{welinder2010caltech}, Oxford-102 flowers \cite{Nilsback08}, and large-scale MSCOCO \cite{lin2014microsoft}. In complement of existing evaluation metric (e.g. Inception score \cite{improvedGAN}) for generative models, we also introduce a new visual-semantic similarity metric to evaluate the alignment between generated images and conditioned text. Extensive experimental results and analysis demonstrate the effectiveness of our method and significantly improved performance compared against previous state of the arts on all three evaluation metrics.

@@

\section{Related Work}
%We discusse related work and further clarify the novelty of our method by comparing with them.

@@

Text-to-image synthesis is an interesting application of GANs. Reed \etal \cite{reed2016generative}  first introduce a method that can generate $64^2$ resolution images, which is similar with DCGAN \cite{radford2015unsupervised}. This method presents a new strategy for image-text matching aware adversarial training. Reed \etal \cite{reed2016learning} propose a generative
adversarial what-where network (GAWWN) to enable location and content instructions in text-to-image synthesis. StackGAN \etal \cite{han2017stackgan} propose a two-stage stacking GAN training approach that is able to generate $256^2$ compelling images. Recently, Dong \etal \cite{dong2017semantic} propose to learn a joint embedding of images and text so as to re-render a prototype image conditioned on a targeting description. Cha \etal \cite{char2017perceptual} explore the usage of the perceptional loss \cite{johnson2016perceptual} with a CNN pretrained on ImageNet  and Dash \etal \cite{dash2017tac} make use of auxiliary classifiers (similar with \cite{odena2016conditional}) to assist GAN training for text-to-image synthesis.

Learning a continuous mapping from a low-dimensional embedding manifold to a complex real data distribution is a long-standing problem. Although GANs have made significant progress, there are still many unsolved difficulties, e.g. training instability and high-resolution generation. Wide methods have been proposed to address the training instability, such as various training techniques \cite{salimans2016improved,arjovsky2017wasserstein,berthelot2017began,shrivastava2016learning,odena2016conditional}, regularization using extra knowledge (e.g. image labels, ImageNet CNNs, etc) \cite{dosovitskiy2016generating,ledig2016photo,dash2017tac,dash2017tac}, or different generator and discriminator combinations  \cite{metz2016unrolled,durugkar2016generative,yang2017lr,huang2016stacked}. \textit{While our method shows a new way to unite generators and discriminators and does not requires any extra knowledge apart from training paired text and images.} In addition, it is easy to see the training difficulty increases significantly as the targeting image resolution increases.

@@

To synthesize high-resolution images, cascade networks are effective to decompose originally difficult tasks to multiple subtasks (Figure \ref{fig:archs-review} A).
Denton \etal \cite{denton2015deep} train a cascade of GANs in a Laplacian pyramid framework (LAPGAN) and use each to synthesize and refine image details and push up the output resolution stage-by-stage. StackGAN also shares some similar idea with LAPGAN. Inspired by this strategy, Chen \etal \cite{chen2017photographic} present a cascaded refinement network to synthesize high-resolution scene from semantic maps. 
%%% Huang \etal \cite{huang2016stacked} propose a top-down stacked GAN to leverage mid-level representations, which shares some similarities with StackGAN and our method. However, this method needs multiple symmetric bottom-up pre-trained discriminators and the usage for high-resolution image is unclear. 
Recently, Karras \etal \cite{Karras2017progressive} propose a progressive training of GANs. The idea is to add symmetric generator and discriminator layers gradually for high-resolution image generation (Figure \ref{fig:archs-review} C). \textit{Compared with these strategies that train low-to-high resolution GANs stage-by-stage or progressively, our method has the advantage of leveraging mid-level representations to encourage the integration of multiple subtasks, which makes end-to-end high-resolution image synthesis in a single vanilla-like GAN possible.}

@@

\subsection{Adversarial objective basics}
In brief, a GAN \cite{goodfellow2014generative} consists of a generator $G$ and a discriminator $D$, which are alternatively trained to compete with each other. $D$ is optimized to distinguish synthesized images from real images, meanwhile, $G$ is trained to fool $D$ by synthesizing fake images. Concretely, the optimal $G$ and $D$ can be obtained by playing the following two-player min-max game,

\begin{equation}
\label{equ:GAN}
\begin{split}
G^*, D^* = \arg~\underset{G}{\min}\ \underset{D}{\max}~ \mathcal{V}(D, G, Y, \bm z),
\end{split}
\end{equation}
where $Y$ and $\bm z \sim \mathcal{N}(0,1)$ denote training images and random noises, respectively. 
%$G$ is learned to approximate $G(\bm z) \sim p(Y)$.  The loss $\mathcal{L}$ for the valuation function is usually a cross-entropy loss, such that $\mathcal{V}(\cdot) = - \mathcal{L}(\cdot)$. 
$\mathcal{V}$ is the overall GAN objective, which usually takes the form $\mathbb{E}_{Y\sim p_{data}}\big[\log D(Y)\big] + \mathbb{E}_{\bm z\sim p_{z}}\big[\log (1-D(G(\bm z)))\big]$ (cross-entropy loss) or other variations \cite{lsgan,berthelot2017began}.

@@

The proposed $\mathcal{G}$ is a CNN (defined in Section 3.4) producing multiple outputs with gradually increasing size:
%This architecture resemble the proposed inverse architectures in edge detection\cite{xie2015holistically} and classification \cite{lee2015deeply}, which demonstrate that additional supervision to hidden layers can improve model generalization and boost optimization.  
\begin{equation}
\label{side}
X_1,..., X_s = \mathcal{G}(\bm t, \bm z), 
\end{equation}
where  $\bm t\sim p_{data}$ denotes a sentence embedding (generated by a pre-trained char RNN text encoder\cite{reed2016generative}). $\mathcal{G}$ produces $s-1$ side outputs $\{X_1,...,X_{s-1}\}$  and one final output $X_s$ with the highest resolution.

@@

For each side output $X_i$ from the generator, a distinct discriminator $D_i$ is associated to compete with it. Therefore, our full min-max objective is defined as 
\begin{equation}
\label{equ:optim}
\begin{split}
  \mathcal{G}^*, \mathcal{D}^*&  =  \arg~\underset{\mathcal{G}}{\min}\ \underset{\mathcal{D}}{\max}~ \mathcal{V}(\mathcal{G},\mathcal{D}, \mathcal{Y}, \bm t, \bm z), \\
  %\text{where} \;\;	 \mathcal{D} & =  \{D_1, ..., D_s\}, \; \mathcal{Y} = \{Y_1, ..., Y_s\},
\end{split}
\end{equation}
where $\mathcal{D}  =  \{D_1, ..., D_s\} $ and $\; \mathcal{Y} = \{Y_1, ..., Y_s\}$ denotes one training image at multi-scales, $\{1,...,s\}$, forming an image pyramid.
Compared with Eq. (\ref{equ:GAN}), our generator competes with multiple discriminators  $\{D_i\}$ at different hierarchies (Figure \ref{fig:archs-review} D), each focuses on learning discriminative features in different contextual scale.

In principle, the lower-resolution side output is used to learn semantic consistent image structures (e.g. object shape, colors, and background), and the subsequent higher-resolution side outputs are used to render fine-grained details. Since our method is trained in an end-to-end fashion, the lower-resolution outputs can also fully utilize top-down knowledge from discriminators at higher resolutions. As a result, we can observe consistent image structures, color and styles in outputs of both low and high resolutions without using addition regularization terms.

%Since our method is trained in an end-to-end manner, the lower-resolution side outputs can fully enjoy the top-down knowledge from higher resolutions, such that we can observe consistent image structures and styles appear in both low and high resolutions.
%The experiment demonstrates this advantage compared with StackGAN. 
% % According to our empirical observation, our design is able to reduce the model instability, especially at the early stage of the training.
%% %We present the following multi-purpose adversarial loss to support more effective generator training.

\subsection{Multi-purpose adversarial losses}
Our generator produces resolution-growing side outputs composing an image pyramid. 
We leverage this hierarchy property and allow adversarial losses to capture hierarchical image statistics, with a goal to guarantee both semantic consistency and image fidelity.

In order to guarantee semantic consistency, we adopt the matching-aware pair loss proposed by \cite{reed2016generative}. The discriminator is designed to take image-text pairs as inputs and be trained to identify two types of errors: a real image with mismatched text and a fake image with conditioned text.

The pair loss is designed to guarantee the global semantic consistency. However, there is no explicit loss to guide the discriminator to differentiate real images from fake images. And combining both tasks (generating realistic images and matching image styles with text) into one network output complicates the already challenging learning tasks. Moreover, as the image resolution goes higher, it might be challenging for a global pair-loss discriminator to capture the local fine-grained details (results are validated in experiments).
%As the image resolution goes higher, discriminators might loss focus for local fine-grained image details.
%However, this loss has two major weaknesses. First, there is no explicit loss that force the discriminator to differentiate real images from fake images. 
%Combining both tasks (generating realistic images and matching image with text) into one output further complicates the learning tasks, which is already challenging. 
%Second, as the image resolution goes higher, it might be challenging for a global pair-loss discriminator to capture local fine-grained details.  
In addition, as pointed in \cite{shrivastava2016learning}, a single global discriminator may over-emphasize certain biased local features and lead to artifacts.

To alleviate these issues and guarantee image fidelity, our solution is to add local adversarial image losses.
%as inspired by \cite{shrivastava2016learning}. 
%The insights are two folds:
%\begin{itemize}\vspace{-.1cm}
%\setlength\itemsep{-0.3em}
%\item Further forcing the generated samples to have only only global but also local similar statistics to real image patches, which is beneficial for rendering fine-grained details. 
%
%\item \textcolor{red}{Image loss without using paired text can be beneficial in the sense that it focus more on image information. The richness of discriminator supervision usually has advantages for generalization. } 
%\vspace{-.2cm}
%\end{itemize}
We expect the low-resolution discriminators to focus on global structures, while the high-resolution discriminators to focus  on local image details.
Each discriminator $D_i$ consists of two branches (see Section 3.4), one computes a single scalar value for the pair loss and another branch computes  $R_i{\times}R_i$ 2D output maps $O_i$ for local image loss.
%with an extra branch of the discriminator for the pair loss (see Section 3.4).
%computes a $R{\times}R$ probability map. 
Each element in $O_i$ differentiates whether a corresponding local image patch is real or fake.
For each $D_i$, we control $R_i$ accordingly to tune the receptive field of each element of $O_i$. 
%In practice, the local image adversarial loss can be implemented as an fully CNN \cite{shrivastava2016learning,zhu2017unpaired,isola2016image}. 
Figure \ref{fig:loss} illustrates how hierarchically-nested discriminators compute the two losses on the generated images in the pyramid.

%Specifically, a larger $R_i$ value results in a smaller local range and finer focus of discriminators.

\begin{figure}[t]
	\centering
	\includegraphics[width=0.49\textwidth]{figure/loss.pdf}
	\vspace{-.7cm}
	\caption{Given a set of images from the side output pyramid of the generator, the corresponding discriminator $D_i$ computes the matching-aware pair loss and local image loss (outputting a $R_i{\times}R_i$ probability map to classify real or fake image patches). }  \vspace{-.2cm}
	\label{fig:loss}
\end{figure}

\textbf{Full Objective } Overall, our full min-max adversarial objective can be defined as 
%%hierarchically-nested discriminators $\{D_i\}$ optimize the following objective:
\vspace{-.2cm}
\begin{equation}
\begin{split}
\mathcal{V}(& \mathcal{G},\mathcal{D}, \mathcal{Y}, \bm t, \bm z) = \sum_{i=1}^{s} \Big(  L_2\big(D_i({Y}_i)\big) +  L_2\big(D_i({Y}_i, \bm t_{Y})\big) \, + \\ 
& \overline{L_2}\big(D_i({X}_i)\big)  + \overline{L_2}\big(D_i({X}_i, \bm{t}_{X_i})\big) + \overline{L_2}\big(D_i({Y}_i,  \bm{t}_{\overline{Y}})\big) \Big),
\end{split}
\end{equation}
where $L_2(x) = \mathbb{E}\big[(x - \mathbb{I})^2\big]$ is the mean-square loss (instead of the conventional cross-entropy loss) and $\overline{L_2}(x) =\mathbb{E}\big[x^2\big]$. 
This objective is directly minimized by $\mathcal{D}$. For generator $\mathcal{G}$ in practice, we minimize 
$\sum_{i=1}^{s} (L_2(D_i(\mathcal{G}(\bm t, \bm z)_i)) +  L_2\big(D_i(\mathcal{G}(\bm t, \bm z)_i, \bm{t}_{X_i})))$ instead.
For the local image loss, the shape of $x, \mathbb{I} \in \mathbb{R}^{R_i{\times}R_i}$ vary accordingly (see Figure \ref{fig:loss}). $R_i=1$ refers to the (largest local) global range. $D_i(X_i)$ is the image loss branch and $D_i(X_i, \bm{t}_{X_i})$ is the pair loss branch (conditioned on $\bm{t}_{X_i}$).
$\{Y_i, \bm t_{Y}\}$ denotes a matched image-text pair and $\{Y_i, \bm{t}_{\overline{Y}}\}$ denotes a mismatched image-text pair.

In the spirit of variational auto-encoder \cite{vae} and the practice of StackGAN \cite{han2017stackgan}, instead of directly using the deterministic text embedding, we sample a stochastic vector from a Ganssian distribution $\mathcal{N}(\mu({\bm t}), \Sigma({\bm t}))$, where $\mu$ and $\Sigma$ are parameterized functions of $\bm t$. 
We add the Kullback-Leibler divergence regularization term, $D_{KL}(\mathcal{N}(\mu({\bm t}), \Sigma({\bm t}) )|| \mathcal{N}(0, \bm{I}))$, to the GAN objective to prevent over-fitting and force smooth sampling over the text embedding distribution.

@@

\textbf{Generator} The generator is simply composed of three kinds of modules, termed as $K$-repeat res-blocks, stretching layers, and linear compression layers.
A single res-block in the $K$-repeat res-block is a modified\footnote{We remove ReLU after the skip-addition of each residual block, with an intention to reduce sparse gradients.} residual block \cite{he2016identity}, which contains two convolutional (conv) layers (with batch normalization (BN) \cite{ioffe2015batch} and ReLU). The stretching layer serves to change the feature map size and dimension. It simply contains a scale-$2$ nearest up-sampling layer followed by a conv layer with BN+ReLU. The linear compression layer is a single conv layer followed by a Tanh to directly compress feature maps to the RGB space (as side outputs). We prevent any non-linear function in the compression layer that could impede the gradient signals. 
%, whose compact design enforces feature maps in conv blocks can linearly represent RGB images at arbitrary scales.
Starting from a $1024{\times}4{\times}4$ embedding, which is computed by CA and a trained embedding matrix, the generator simply uses $M$ $K$-repeat res-blocks connected by $M{-}1$ in-between stretching layers until the feature maps reach to the targeting resolution. 
For example, for $256{\times}256$ resolution and $K{=}1$, there are $M{=}6$ $1$-repeat res-blocks and $5$ stretching layers. 
%Such simple and symmetric design makes our generator helpful for gradient flows. We will verify in experiments. 
At pre-defined side-output positions at scales $\{1,...,s\}$, we apply the compression layer to generate side output images, for the input of the discriminator.
